Functional oxide layers for electrical isolation and chemical passivation of steel substrates

### 2023-02-26 Thesis/chapter/030-theory-materials.tex
change from article to report

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Photovoltaics}
%\subsubsection{Problems of current energy supply}
The world wide energy consumption has more than doubled between 1970 and 2015\cite{BP2017} 
and according to recent studies both fossil\cite{BGR2017} and uranium sources\cite{Uran2006} 
will be exhausted within the next 100 years. 
Even though this time period is not exact and highly dependent on detection methods of resources, 
this number is rather small and brings us in \textit{zugzwang} to develop sustainable energy sources. 
One viable option is \gls{pv}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{History of Photovoltaics}
The photoelectric effect was first described in 1839 by french scientist Alexandre 
Edmond Becquerel\cite{becquerel1839memoire}, the father of Henri Becquerel (the person after whom the unit is named).
Another relevant piece of the \gls{pv} jigsaw was brought to light
%discovered
with the discovery of photo conductivity of selenium
by British engineer Willouhgby Smith\cite{Smith1873Selenium}.
In 1876 William Adams and Richard Day\cite{Adams1876Selenium} showed that 
the energy of light can be directly converted into electrical energy by a bar of 
selenium with attached platinum electrodes.
And finally, in 1905 Einstein described the physical background of the photoelectric 
effect with his light quantum theory\cite{einstein1905erzeugung}.
In the 1950s the first solar cells (with efficiencies under 10 percent) were used in niche applications such as space flight. 
Eventually, the interest in photovoltaic and other alternative energy sources 
rose - fuelled by the oil crisis in 1973 - 
and the development of photovoltaic for the consumer market was boosted. 
This development lead to a drop in 
average price for \gls{pv} module from \$ 100 per watt in 1975 to \$ 4 per watt in 2007\cite{pagliaro2008flexible}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Photovoltaics Basics}
The process of conversion of photons into voltaic energy can be broken down into two essential steps (both in silicon based \gls{pv} or in plants): 
the creation of an electron-hole pair and then its separation by the structure of the material.\cite{markvart2013principles}
This means that \gls{pv} cells are basically diodes, which have a low resistance in one direction and a high resistance in the other direction. 
This is often achieved through a p-n junction.
The n-type side has excess electrons and p-type side has excess electron holes. 
If the n- and p-type are of the same basis material, they are called homojunctions (e.g. silicon); if not, heterojunctions e.g. \ch{CdS}/\gls{cigs} and \ch{CdS/CdTe}.\cite{breitenstein2013understanding}
%
The first marketable \gls{pv} were crystalline silicon photovoltaic modules which still 
have the biggest market share in the \gls{pv} segment (including polycrystalline and monocrystalline silicon).
In 2022 
over 88\% of all sold \gls{pv} where made of silicon (including amorphous silicon).\cite{breitenstein2013understanding}
%
A comprehensive overview on different \gls{pv} technologies can be found in \cite{markvart2013principles}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{CIGS}
\gls{cigs} (\ch{CuIn_{x}Ga_{1-x}Se2}) is of the chalcopyrite (\ch{CuFeS2}) group (tetragonal crystal system). 
%It was 
\ch{CuInSe2} and \ch{CuGaSe2} were first synthesised in 1953 by Harry Hahn et al.\cite{hahn1953untersuchungen}.
The potential use of \ch{CuInSe2} as \gls{pv} material in combination with \ch{CdS} was first mentioned in 1974\cite{wagner1974cuinse2}.
%Already in 1975 efficiencies of cells of over 10\% were achieved.\cite{kazmerski1976thin}
Cells with efficiencies of over 10\% were achieved already by 1975.\cite{kazmerski1976thin}
Today, 
\gls{cigs} modules (multiple \gls{pv} cells in series) 
reach efficiencies of up to 16\%\cite{feurer2017cigs},
monocrystalline silicon \gls{pv} modules reach efficiencies of 14-20\%
and polycrystalline silicon \gls{pv} modules 12-17\%\cite{mcevoy2011practical}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Materials and Their Analysis}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Zirconium oxide}
Zirconium oxide \gls{zro} is a ceramic with a band gap of 5-7 eV and dielectric constant of 15-22 at room temperature\cite{Anwar2017}. 
This makes it attractive as an insulator for semiconductor and \gls{pv} industry. 
It is monoclinic below 1050 °C, tetragonal between 1170 °C and 2370 °C, and cubic above 2370 °C\cite{Nielsen2005}.
The cubic phase can be stabilized down to room temperature by the addition of magnesia (\ch{MgO}), calcia (\ch{CaO}) or yttria (\ch{Y2O3}) which avoids mechanical failing due to shrinkage 
when cooling and undergoing phase transition\cite{Nielsen2005}.
It is very resistant to acids (except \ch{HF} and hot \gls{h2so4}) and alkalis\cite{Nielsen2005}.
Hydrous Zirconium Oxide (\ch{Zr(OH)8 * 16 H2O}) gel can be produced by neutral hydrolysis of sodium zirconate (\ch{NaZrO3})\cite{Nielsen2005}.
%"Zirconium alkoxides hydrolyze quite easily, [providing] a route to high purity, high-surface-area zirconium oxide"\cite{Nielsen2005}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Sol-Gel and Doctor Blading}
%\td{what is it? What is it used for? How does it work? What different kinds are there? }One of the advantages of sol-gel process is that it can be used in roll-to-roll procedures.
%
\Gls{db} coating (also known as tape casting) is widely used in the textile, paper, photographic film, printing, and ceramic industries.
The roll-to-roll compatible process can fabricate highly uniform flat films over large areas\cite{yang2010large}.
A blade is moved over a substrate spreading a slurry at a fixed distance with a fixed velocity.
In roll-to-roll processes the substrate moves instead of the blade.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Photovoltaics}
%\subsection{Problems of current energy supply}
The world wide energy consumption has more than doubled between 1970 and 2015\cite{BP2017} 
and according to recent studies both fossil\cite{BGR2017} and uranium sources\cite{Uran2006} 
will be exhausted within the next 100 years. 
Even though this time period is not exact and highly dependent on detection methods of resources, 
this number is rather small and brings us in \textit{zugzwang} to develop sustainable energy sources. 
One viable option is \gls{pv}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{History of Photovoltaics}
The photoelectric effect was first described in 1839 by french scientist Alexandre 
Edmond Becquerel\cite{becquerel1839memoire}, the father of Henri Becquerel (the person after whom the unit is named).
Another relevant piece of the \gls{pv} jigsaw was brought to light
%discovered
with the discovery of photo conductivity of selenium
by British engineer Willouhgby Smith\cite{Smith1873Selenium}.
In 1876 William Adams and Richard Day\cite{Adams1876Selenium} showed that 
the energy of light can be directly converted into electrical energy by a bar of 
selenium with attached platinum electrodes.
And finally, in 1905 Einstein described the physical background of the photoelectric 
effect with his light quantum theory\cite{einstein1905erzeugung}.
In the 1950s the first solar cells (with efficiencies under 10 percent) were used in niche applications such as space flight. 
Eventually, the interest in photovoltaic and other alternative energy sources 
rose - fuelled by the oil crisis in 1973 - 
and the development of photovoltaic for the consumer market was boosted. 
This development lead to a drop in 
average price for \gls{pv} module from \$ 100 per watt in 1975 to \$ 4 per watt in 2007\cite{pagliaro2008flexible}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Photovoltaics Basics}
The process of conversion of photons into voltaic energy can be broken down into two essential steps (both in silicon based \gls{pv} or in plants): 
the creation of an electron-hole pair and then its separation by the structure of the material.\cite{markvart2013principles}
This means that \gls{pv} cells are basically diodes, which have a low resistance in one direction and a high resistance in the other direction. 
This is often achieved through a p-n junction.
The n-type side has excess electrons and p-type side has excess electron holes. 
If the n- and p-type are of the same basis material, they are called homojunctions (e.g. silicon); if not, heterojunctions e.g. \ch{CdS}/\gls{cigs} and \ch{CdS/CdTe}.\cite{breitenstein2013understanding}
%
The first marketable \gls{pv} were crystalline silicon photovoltaic modules which still 
have the biggest market share in the \gls{pv} segment (including polycrystalline and monocrystalline silicon).
In 2022 
over 88\% of all sold \gls{pv} where made of silicon (including amorphous silicon).\cite{breitenstein2013understanding}
%
A comprehensive overview on different \gls{pv} technologies can be found in \cite{markvart2013principles}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{CIGS}
\gls{cigs} (\ch{CuIn_{x}Ga_{1-x}Se2}) is of the chalcopyrite (\ch{CuFeS2}) group (tetragonal crystal system). 
%It was 
\ch{CuInSe2} and \ch{CuGaSe2} were first synthesised in 1953 by Harry Hahn et al.\cite{hahn1953untersuchungen}.
The potential use of \ch{CuInSe2} as \gls{pv} material in combination with \ch{CdS} was first mentioned in 1974\cite{wagner1974cuinse2}.
%Already in 1975 efficiencies of cells of over 10\% were achieved.\cite{kazmerski1976thin}
Cells with efficiencies of over 10\% were achieved already by 1975.\cite{kazmerski1976thin}
Today, 
\gls{cigs} modules (multiple \gls{pv} cells in series) 
reach efficiencies of up to 16\%\cite{feurer2017cigs},
monocrystalline silicon \gls{pv} modules reach efficiencies of 14-20\%
and polycrystalline silicon \gls{pv} modules 12-17\%\cite{mcevoy2011practical}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Materials and Their Analysis}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Zirconium oxide}
Zirconium oxide \gls{zro} is a ceramic with a band gap of 5-7 eV and dielectric constant of 15-22 at room temperature\cite{Anwar2017}. 
This makes it attractive as an insulator for semiconductor and \gls{pv} industry. 
It is monoclinic below 1050 °C, tetragonal between 1170 °C and 2370 °C, and cubic above 2370 °C\cite{Nielsen2005}.
The cubic phase can be stabilized down to room temperature by the addition of magnesia (\ch{MgO}), calcia (\ch{CaO}) or yttria (\ch{Y2O3}) which avoids mechanical failing due to shrinkage 
when cooling and undergoing phase transition\cite{Nielsen2005}.
It is very resistant to acids (except \ch{HF} and hot \gls{h2so4}) and alkalis\cite{Nielsen2005}.
Hydrous Zirconium Oxide (\ch{Zr(OH)8 * 16 H2O}) gel can be produced by neutral hydrolysis of sodium zirconate (\ch{NaZrO3})\cite{Nielsen2005}.
%"Zirconium alkoxides hydrolyze quite easily, [providing] a route to high purity, high-surface-area zirconium oxide"\cite{Nielsen2005}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Sol-Gel and Doctor Blading}
%\td{what is it? What is it used for? How does it work? What different kinds are there? }One of the advantages of sol-gel process is that it can be used in roll-to-roll procedures.
%
\Gls{db} coating (also known as tape casting) is widely used in the textile, paper, photographic film, printing, and ceramic industries.
The roll-to-roll compatible process can fabricate highly uniform flat films over large areas\cite{yang2010large}.
A blade is moved over a substrate spreading a slurry at a fixed distance with a fixed velocity.
In roll-to-roll processes the substrate moves instead of the blade.
